---
title: "Something about Zomato"
author: "Arion Barzoucas-Evans (s3650046) & Joshua Grosman (insert student number)"
date: "08/08/2018"
output:
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
  html_document:
    df_print: paged
    toc: no
    toc_depth: '3'
linkcolor: blue
header-includes:
     - \usepackage{float}
subtitle: MATH 1298 Analysis of Categorical Data Project Phase I
documentclass: article
bibliography: references.bib
---


\newpage

\tableofcontents

\newpage

# Introduction \label{sec1}


Zomato is a restaurant search and discovery service founded in 2008. Users can access a plethora of information about restuarants listed on Zomato, including information not available on the restaurant's own website. Such information includes the type of cuisine, opening hours, photos of the menu and the restaurant, pricing, and whetheror not the restaurant offers online delivery. Customers that visit the restaurants have the option of reviewing them and giving them a rating from 0 to 5. Higher rated restaurants receive more attention resulting in higher revenues. As such, understanding how users of Zomato rate restaurants is of great interest to restaurant owners in order to improve their business. The aim of this report is to explore the relationship of several factors like price and cuisine with Zomato ratings using publicly available data found on [Kaggle](https://www.kaggle.com/shrutimehta/zomato-restaurants-data). In phase I exploratory data analysis will be performed on the dataset, including data pre-processing, creation of new variables, and visual representation of the data. This will assist in observing and understanding any relationships present in the data. Following this, a logistic regression model will be fitted in phase II in order to predict the probability of receiving certain ratings according to the values of the chosen explanatory variables.

# Data Set

The dataset used in this report was acquired from [Kaggle](https://www.kaggle.com/shrutimehta/zomato-restaurants-data). It contains 9,551 observations each of which corresponds to a different restaurant and contains the following information:

* *Restaurant.ID*: A unique ID assigned to each restaurant.
* *Restaurant.Name*: Name of the restaurant.
* *Country.Code*: Codes corresponding to countries listed in a separate dataset.
* *City*: Name of the city where the restaurant is located.
* *Address*: Address of the restaurant.
* *Locality*: General location of the restaurant (short description).
* *Locality.Verbose*: General location of the restaurant (long description).
* *Longitude*: Longitude of the location of the restaurant (geographic coordinates).
* *Latitude*: Latitude of the location of the restaurant (geographic coordinates).
* *Cuisines*: Type of cuisine offered by the restaurant.
* *Average.Cost.for.two*: Average cost for two people (in the countries respective currency).
* *Currency*: Currency which is used at each restaurant.
* *Has.Table.booking*: Whether the restaurant offers the option to book a table or not.
* *Has.Online.delivery*: Whether the restaurant offers delivery through the internet or not.
* *Is.delivering.now*: Whether the restaurant was delivering at the time the dataset was created or not.
* *Switch.to.order.menu*: Unclear variable with only one level (No) for all observations.
* *Price.range*: Categorised price (between 1 and 4).
* *Aggregate.rating*: Aggregated rating from user votes.
* *Rating.color*: Categorised rating into a colour code.
* *Rating.text*: Response variable. Categorised rating with 6 levels (between Poor to Excellent).
* *Votes*: Number of votes used in the aggregate rating.



\newpage

# Data Preparation


In this project, the following `R` packages were used.

```{r, message = FALSE, warning=FALSE}
library(mlr)
library(data.table)
library(plyr)
library(dplyr)
library(ggplot2)
library(broom)
library(vcd)
library(knitr)
library(kableExtra)
```

```{r, message = FALSE, warning=FALSE, include=FALSE}
# custom str function
str_format <- function(df){
  df_sum = data.frame(Variable = names(df),
                  Class = sapply(df, class),
                  Cardinality = sapply(df, function(x){
                    if(class(x) == "factor"){
                      return(length(levels(x)))
                    }
                    return(length(unique(x)))
                  }),
                  Levels = sapply(df, function(x){
                    if(class(x) == "factor"){
                      return(paste0(head(levels(x)), collapse = ", "))
                    }
                    return(paste0(head(unique(x)), collapse = ", "))
                  }),
                  First_Values = sapply(df, function(x) paste0(head(x),  collapse = ", ")),
                  row.names = NULL) 
  
  colnames(df_sum)[5] = "First Values"
  colnames(df_sum)[4] = "First Levels"
  
  return(df_sum)
}
```


```{r, message = FALSE, warning=FALSE, echo=FALSE, include=FALSE}
zomato = read.csv("zomato.csv")
zomato = as.data.table(zomato)

countries = read.csv("Country-Code.csv")

```

As Table 1 indicates, there are no NA values in any of the features. Additionally, according to Table 2 restaurant ID's are unique for every restaurant while there are appears to be some duplicate restaurant names due to the existance of restaurant chains. Furthermore, each restaurant has multiple cuisines which causes the `cuisine` feature to have so many levels. Finally, the `Switch.to.order.menu` feature only has one level ("No") for the entire dataset.


```{r, message = FALSE, warning=FALSE, echo=FALSE}
kable(as.data.frame(summarizeColumns(zomato)),
      caption = "Feature summary before data preprocessing.",
      format = "latex") %>% kable_styling(latex_options = c("scale_down","HOLD_position"))

```

```{r, message = FALSE, warning=FALSE, echo=FALSE}
zomato_temp = zomato
zomato_temp[,c(2,5:7,10)] = lapply(zomato[,c(2,5:7,10)], strtrim, width = 10)

df = str_format(zomato_temp)

kable(df, caption = "Variable summary for the Zomato dataset\n9551 Observations of 21 Variables",
        format = "latex") %>% kable_styling(latex_options = c("scale_down","HOLD_position"))
```

To rectify the identified issues, all unnecessary features were removed. This includes `Restaurant.ID` (unique identifier), `Restaurant.Name` ,`Address`, `Locality`, `Locality.Verbose`, `Is.delivering.now`, `Switch.to.order.menu`, `City`, `Currency`, `Rating.color`. The `Average.Cost.for.two` is in many different currencies and the concept of what is considered expensive would be affected by socio-economic factors in each country. For this reason this feature was standardised by currency. Furthermore, the `cuisines` variable was separated into 18 new binary features using the most prevalent levels within the original `cuisines` variable. Each of these features indicates the presence or absence of that particular cuisine in the restaurant. This way, restaurants can have multiple cuisines. Using these new binary variables, a new feature, `Cuisine_Range`, was created as the sum of all the cuisine binary variables. The `Cuisine_Range` would indicate the number of different cuisines present in a restaurant which may be of interest to the model in deciding a restaurant's rating. Finally, `Has.Table.booking` and `Has.Online.delivery` were recoded into binary variables, the country table was joined to the Zomato dataset through `Country.Code` and then aggregated into a `Continent` feature. Tables 3 and 4 show the data after preprocessing.

```{r, message = FALSE, warning=FALSE, echo=FALSE}
# Scale cost by currency
zomato[,Average.Cost.for.two.Std := as.vector(scale(Average.Cost.for.two)), by=Currency]

# Reorder columns and remove original cost column
zomato = zomato[,c(1:11,22,12:21)]
zomato = zomato[,Average.Cost.for.two := NULL]

# Create new binary variables for cuisine type (1-C encoding)
splitdat = do.call("rbind", strsplit(as.character(zomato$Cuisines), ","))
unique.cuisines = as.vector(unique(as.vector(trimws(splitdat))))
current.names = as.vector(names(zomato))

new.names = as.vector(matrix(c(current.names,unique.cuisines))) 

for(i in 1:length(unique.cuisines)){
  zomato[,paste(i)] = rep(0,nrow(zomato))
}

names(zomato) = new.names

for(i in 1:length(unique.cuisines)){
zomato[,unique.cuisines[i]] = ifelse(grepl(unique.cuisines[i],zomato$Cuisines),1,0)
}


# Aggregate new variables 
zomato = zomato[, `:=`(European = French+European+Italian+German+
                                  Mediterranean+Greek+Spanish+Irish+
                                  British+Portuguese+Scottish+Belgian,
                       Asian = Japanese+Chinese+Asian+Filipino+Korean+
                               Vietnamese+Thai+Singaporean+Malaysian+
                               Indonesian+Taiwanese+Cantonese+Malay+
                               Peranakan+Sunda,
                       `South American` = Brazilian+Mexican+Peruvian+
                                          `Latin American`+Caribbean+
                                          Cuban+`South American`+Argentine+
                                          Mineira,
                       Indian = Indian+Goan+`South Indian`+`North Indian`+
                                Rajasthani+Mughlai+Mithai+Maharashtrian+
                                `Modern Indian`+Biryani+Parsi+Kashmiri+
                                Bengali+Awadhi+Lucknowi+Gujarati+Oriya+
                                Hyderabadi+Bihari+Kerala+Andhra+Malwani+
                                Assamese+Naga+Chettinad+Mangalorean,
                       American = American+Hawaiian+`New American`+Cajun+Canadian,
                       `Middle Eastern` = `Middle Eastern`+Arabian+Lebanese+
                                          Turkish+Pakistani+Persian+Burmese+Tibetan+
                                          Afghani+Nepalese+Iranian+Izgara+Armenian+Durban,
                       Other = `Bar Food`+International+Steak+BBQ+Southern+Breakfast+
                               Sandwich+`Modern Australian`+African+`North Eastern`+`Tex-Mex`+
                               `Cuisine Varies`+`Charcoal Grill`+`Asian Fusion`+Kiwi+Contemporary+
                               Ramen+Grill+`Sri Lankan`+Kebab+`World Cuisine`+`Turkish Pizza`+
                               `Restaurant Cafe`+Southwestern+Diner+Teriyaki+Vegetarian+
                               Fusion+Deli+`Fish and Chips`+`Dim Sum`+Curry+`South African`+
                               Bí_rek+`Soul Food`+Moroccan+Dí_ner+`Pub Food`+Tapas+Western+
                               Australian+Sushi+Salad,
                       Desserts = Desserts+`Ice Cream`+Patisserie,
                       `Fast Food` = `Fast Food`+`Gourmet Fast Food`,
                       Beverages = Beverages+Juices+`Coffee and Tea`+Tea+`Drinks Only`+`Bubble Tea`)]

zomato = zomato[, `:=`(French=NULL,Italian=NULL,German=NULL,
                    Mediterranean=NULL,Greek=NULL,Spanish=NULL,Irish=NULL,
                    British=NULL,Portuguese=NULL,Scottish=NULL,Belgian=NULL,
                    Japanese=NULL,Chinese=NULL,Filipino=NULL,Korean=NULL,
                    Vietnamese=NULL,Thai=NULL,Singaporean=NULL,Malaysian=NULL,
                    Indonesian=NULL,Taiwanese=NULL,Cantonese=NULL,Malay=NULL,
                    Peranakan=NULL,Sunda=NULL,
                    Brazilian=NULL,Mexican=NULL,Peruvian=NULL,
                    `Latin American`=NULL,Caribbean=NULL,
                    Cuban=NULL,Argentine=NULL,Mineira=NULL,
                    Goan=NULL,`South Indian`=NULL,`North Indian`=NULL,
                    Rajasthani=NULL,Mughlai=NULL,Mithai=NULL,Maharashtrian=NULL,
                    `Modern Indian`=NULL,Biryani=NULL,Parsi=NULL,Kashmiri=NULL,
                    Bengali=NULL,Awadhi=NULL,Lucknowi=NULL,Gujarati=NULL,Oriya=NULL,
                    Hyderabadi=NULL,Bihari=NULL,Kerala=NULL,Andhra=NULL,Malwani=NULL,
                    Assamese=NULL,Naga=NULL,Chettinad=NULL,Mangalorean=NULL,
                    American=NULL,Hawaiian=NULL,`New American`=NULL,Cajun=NULL,Canadian=NULL,
                    `Middle Eastern`=NULL,Arabian=NULL,Lebanese=NULL,
                    Turkish=NULL,Pakistani=NULL,Persian=NULL,Burmese=NULL,Tibetan=NULL,
                    Afghani=NULL,Nepalese=NULL,Iranian=NULL,Izgara=NULL,Armenian=NULL,Durban=NULL,
                    `Bar Food`=NULL,International=NULL,Steak=NULL,BBQ=NULL,Southern=NULL,Breakfast=NULL,
                    Sandwich=NULL,`Modern Australian`=NULL,African=NULL,`North Eastern`=NULL,`Tex-Mex`=NULL,
                    `Cuisine Varies`=NULL,`Charcoal Grill`=NULL,`Asian Fusion`=NULL,Kiwi=NULL,Contemporary=NULL,
                    Ramen=NULL,Grill=NULL,`Sri Lankan`=NULL,Kebab=NULL,`World Cuisine`=NULL,`Turkish Pizza`=NULL,
                    `Restaurant Cafe`=NULL,Southwestern=NULL,Diner=NULL,Teriyaki=NULL,Vegetarian=NULL,
                    Fusion=NULL,Deli=NULL,`Fish and Chips`=NULL,`Dim Sum`=NULL,Curry=NULL,`South African`=NULL,
                    Bí_rek=NULL,`Soul Food`=NULL,Moroccan=NULL,Dí_ner=NULL,`Pub Food`=NULL,Tapas=NULL,
                    Western=NULL,Australian=NULL,Sushi=NULL,`Ice Cream`=NULL,Patisserie=NULL,
                    `Gourmet Fast Food`=NULL,Salad=NULL,Juices=NULL,`Coffee and Tea`=NULL,
                    Tea=NULL,`Drinks Only`=NULL,`Bubble Tea`=NULL)]


# Make variables binary again
for(j in names(zomato)[-c(1:21)]){
  set(zomato, i= which(zomato[[j]]>1), j= j, value= 1)
}   

# Map country code to country
zomato = merge(zomato,countries,by = "Country.Code")
zomato = zomato[,Country.Code := NULL]

# Remove remaining unnecessary variables
zomato = zomato[,c("Restaurant.ID","Restaurant.Name","Address",
                   "Locality","Locality.Verbose","Cuisines",
                   "Is.delivering.now","Switch.to.order.menu",
                   "City","Currency","Rating.color"):=NULL]


#Converting yes/no cols to numeric
zomato$Has.Table.booking <- revalue(zomato$Has.Table.booking, c("No"=0, "Yes"=1))
zomato$Has.Online.delivery <- revalue(zomato$Has.Online.delivery, c("No"=0, "Yes"=1))

#Aggregating country into continent(maybe leave india on its own?)
Europe <- c("United Kingdom")
North_America <- c("United States","Canada")
Asia <- c("India","Indonesia","Singapore","Sri Lanka","UAE","Phillipines","Qatar")
Oceania <- c("Australia", "New Zealand")
ROW <- c("Brazil","South Africa", "Turkey")

zomato$continent = zomato$Country

levels(zomato$continent)[levels(zomato$continent) %in% Europe] = "Europe"
levels(zomato$continent)[levels(zomato$continent) %in% North_America] = "North America"
levels(zomato$continent)[levels(zomato$continent) %in% Asia] = "Asia"
levels(zomato$continent)[levels(zomato$continent) %in% Oceania] = "Oceania"
levels(zomato$continent)[levels(zomato$continent) %in% ROW] = "Rest of World"

zomato$Country<-NULL

#converting continent to binary
setDT(zomato)[, c(levels(zomato$continent), "continent") := 
            c(lapply(levels(continent), function(x) as.integer(x == continent)), .(NULL))]

#creating new variable for range of cuisine

zomato$Cuisine_Range = rowSums(zomato[,10:27])

```


```{r, message = FALSE, warning=FALSE, echo=FALSE}
kable(as.data.frame(summarizeColumns(zomato)),
      caption = "Feature summary after data preprocessing.",
      digits = 3) %>% 
  kable_styling(latex_options = c("scale_down","HOLD_position"))

```

```{r, message = FALSE, warning=FALSE, echo=FALSE}
cols <- names(zomato)[1:3]
df = str_format(zomato[,(cols) := round(.SD,3), .SDcols=cols])

kable(df, caption = "Variable summary for the Zomato dataset after preprocessing\n9551 Observations of 21 Variables",
        format = "latex") %>% kable_styling(latex_options = c("scale_down","HOLD_position"))
```

```{r, message = FALSE, warning=FALSE, echo=FALSE}
# get column tables after cleaning
col.freq = list()
for (i in (1:ncol(zomato))){
  col.freq[[i]] = table(zomato[,..i], dnn = colnames(zomato)[i])
}

col.freq[c(4:6,8,10:33)] %>% kable(caption = "Contingency tables for discrete and categorical variables.",
                                  format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = "HOLD_position")
```


# Data Visualisation

#Univariate and Bivariate

Initially, the proportions of the different levels of the rating response variable were examined.

```{r}
prop = table(zomato$Rating.text) %>% prop.table() %>% as.data.frame()
prop$Freq = prop$Freq*100

ggplot(data = prop, aes(x = factor(1), y = Freq, fill = Var1)) +
  geom_bar(stat="identity",width = 1) + coord_polar(theta = "y") +
  ditch_the_axes +
  labs(fill = "Rating", title = "Figure 1. Restaurant Rating Percentage Distribution") +
  geom_text(aes(label = paste(round(Freq,2),"%")), position = position_stack(vjust = 0.5)) 

```

Here it can be seen that the majority of restaurant ratings in the dataset were average. Only a small portion received a rating of either poor or excellent. Furthermore, more than 20% of restaurants in the dataset were not rated. (filter?)

...WORLD MAP...

Next, the average cost of meal was considered with respect to ratings.

```{r}
ggplot(zomato, aes(x=Average.Cost.for.two.Std)) +   
  geom_histogram(aes(y=..density..)) + 
  geom_density(aes(y=..density..),fill="lightpink3",alpha=.5)+
  facet_wrap(~Rating.text)+
  theme_minimal()+labs(title="Figure 2. Standardised Average Cost for Two by Rating",
                       x="Standardised Avergage Cost",
                       y="Density")
```

From this it is clear that restaurants with good, very good and excellent ratings all seem to have a similar distribution of average cost, with the average meal cost for many of these restaurants being quite expensive. This characteristic is not as clear in the other levels, which are more normal in appearance. This suggests that higher rating restaurants are more expensive.

The proportions of ratings according to whether or not the restaurant had the option for table booking is shown below in Figure 3.

```{r}
table_rate <- table(zomato$Has.Table.booking,zomato$Rating.text, dnn = c("Table Booking","Rating"))
prop.table_rate<-data.frame(prop.table(table_rate,1))
colnames(prop.table_rate) <- c("Table Booking","Rating","Proportion")

p1<-ggplot(prop.table_rate,aes(x=`Table Booking`,y=Proportion,fill=Rating))
p1+geom_bar(stat="identity",position="dodge")+
  labs(title="Figure 3. Proportions of Rating by Table Booking Status") +
  theme_minimal()
```

The option of booking a table can be seen to have some effect on the rating of a restaurant with restaurants which do offer table booking having higher propotions of good and very good ratings.

A similar visualisation was used to compare the effect of having online delivery with regard to ratings.

```{r}
del_rate <- table(zomato$Has.Online.delivery,zomato$Rating.text, dnn = c("Online Delivery","Rating"))
prop.del_rate<-data.frame(prop.table(del_rate,1))
colnames(prop.del_rate) <- c("Online Delivery","Rating","Proportion")

p2<-ggplot(prop.del_rate,aes(x=`Online Delivery`,y=Proportion,fill=Rating))
p2+geom_bar(stat="identity",position="dodge")+
  labs(title="Figure 4. Proportions of Rating by Online Delivery Status") +
  theme_minimal()
```

Figure 4 suggests that having the option of online delivery has little effect on restaurant ratings (aside from restaurants which do not have the online delivery being more likely to not be rated).

Next, the amount of customer votes each restaurant received was considered alongside rating. Due to issues with scale, the log transformation was applied to customer votes.

```{r}
ggplot(data = zomato, aes(x = Rating.text, y = log(Votes+1))) +
  geom_boxplot(fill = "lightpink3") + theme_minimal() +
  labs(x = "Rating",
       title = "Figure 5. Log of Customer Votes by Restaurant Rating",
       y="Log of Votes")
```

Here, a trend can be observed wherein higher ratings appear to be associated with more votes. This trend is however disrupted for restaurants which receive an average rating. This maybe due to customers being more likely to convey their underwhelming experiences at a poor-rated restaurant than mediocre experiences at an average-rated restaurant.

The continent the restuarant was located in was then considered. Figure 6 below depicts a world map of the location of all restaurants within the dataset. Figure 7 then considers the proportional distribtuion of ratings across the continents.

```{r}
WorldData <- map_data('world')
WorldData <- WorldData %>% filter(region != "Antarctica")
WorldData <- tidy(WorldData)


p <- ggplot()
p <- p + geom_map(data=WorldData, map=WorldData,
                  aes(x=long, y=lat, group=group, map_id=region),
                  fill="antiquewhite", colour="#7f7f7f", size=0.5) +
  geom_point(data = zomato, aes(x = Longitude, y = Latitude),colour = "red4") +
  coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90)) +
  scale_y_continuous(breaks=c()) +
  scale_x_continuous(breaks=c()) +
  labs(fill="legend", title="Figure 6. Restaurant Locations", x="", y="") +
  theme_bw() +
  theme(panel.border = element_blank())
```
```{r}
cont_rate <- table(zomato$continent,zomato$Rating.text, dnn = c("Continent","Rating"))
prop.cont_rate<-data.frame(prop.table(cont_rate,1))
colnames(prop.cont_rate) <- c("Continent","Rating","Proportion")

p5<-ggplot(prop.cont_rate,aes(x=Continent,y=Proportion,fill=Rating))
p5+geom_bar(stat="identity",position="dodge")+
  labs(title="Figure 7. Proportions of Rating within Continent") +
  theme_minimal()
```

...Map Interpretation...

Inspection of the relative proportions of ratings within each continents highlights that despite being overrepresented in the data, Asian restaurants have relatively low proportions of very good and excellent rated restaurants in comparison to other continents. (Asia has the highest proprotion of not rated restaurants), while Oceana has approximately 66% of ratings at the very good or excellent levels.

The type of restaurant cuisine was then considered with respect to ratings. Here, the continous rating variable was used for simplicity and interpretability. 

```{r}
ggplot(data = zomato, aes(y = Aggregate.rating, x = "")) +
  geom_boxplot(fill = "lightpink3") + facet_wrap(~cuisine, ncol = 6) +
  theme_minimal() + labs(title = "Figure 8. Aggregate Restaurant Rating by Cuisine",
                         y = "Aggregate Rating",
                         x = "Cuisine")
```

From this, it is clear that almost all cuisines are centered around an aggregate rating of 3 to 4, which would equate to ratings of good and very good, respectively. Furthermore, most cuisine types appear to have very little variablity, however others, such as bakery, beverages, street food and raw meats are shown to have a very large interquartile range. This suggests high variability in the aggregate ratings of these kinds of restaurants.

#Multivariate

# Summary

\newpage

# References

---
nocite: | 
  @mlr, @data.table, @dplyr, @plyr, @ggplot2, @broom,  @vcd, @knitr, @kableExtra,
...


